The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-14 document/ms.tex
FP text

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}

@@

Various configurations of grazing or blended eclipsing binaries can mimic the
signal of a transiting planet \citep{}. The occurrence rate calculation
presented in the preceding section assumes that none of the planet
candidates identified in this work are caused by such astrophysical false
positives.  In this Section we explore the validity of this assumption.

>>>>

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}
\newcommand{\exosyspop}{\project{exosyspop}}

@@

Various configurations of eclipsing binary stars can mimic the signal of a
transiting planet \citep{}.  However, the occurrence rate calculation
presented in the preceding section assumes no astrophysical false positives
among the candidates identified in this work.  In this Section we explore the
validity of this assumption.

While an eclipsing binary (EB) typically produces a photometric dip much
deeper than a transiting planet, the depth of the signal may be comparable to
that of a planet if the eclipse is grazing, or if the EB only comprises a small
fraction of the total light in the photometric aperture---a so-called blended
eclipsing binary (BEB).  Additionally, if a binary star has an eccentric
orbit, it may be oriented so as to present only a secondary occultation and
not a primary eclipse, causing a shallow and potentially flat-bottomed
photometric dip without an accompanying tell-tale deep primary signal.

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the python
package \exosyspop\ \citep{Morton:2016b}, which we developed for this
purpose.

With \exosyspop\, one can define the parameters of a population model and
generate synthetic catalogs according to the model (and the parameters of a
survey) very efficiently.  For example, a population of EBs may be defined by
a binary fraction, power-law distributions in mass ratio and period (within
given bounds), and a beta distribution for eccentricity.  This population,
initialized with a catalog of target stars (each of which has a duty cycle and
total span of observation), may then be ``observed,'' returning a catalog of
objects potentially detectable via either primary or secondary eclipse
(according to randomly oriented orbital geometries).  This synthetic catalog
includes signal-to-noise estimates of both the primary and secondary eclipses,
the number of detected primary and secondary eclipses, and the trapezoidal
shape parameters (depth, duration, and ingress-to-duration ratio, as defined
in \citet{Morton:2012}) of each detection.

In order to predict how many EBs or BEBs we might expect to detect in this 
particular search of \kepler\ data, we first need to choose reasonable parameters
for the binary star population.  To do this, we calibrate the population 
parameters using the catalog of detected \kepler\ eclipsing binaries.  We
find that a binary fraction of 15\% between periods of 20 days and 25 years, with
periods distributed as $f(P) \sim P^{-1.1}$ and eccentrities distributed according
to $\beta(0.8, 2.0)$ is able to reproduce well both the number and period 
distribution of

The \kepler\
EB catalog contains 698 EBs with periods between 20 and 1000 days

The first step in determining EBs and BEBs

The scenarios typically considered in \kepler\ false positive analysis
\citep[][e.g.]{Morton:2016} are unblended eclipsing binary stars (EB),
background/foreground chance-aligned eclipsing binaries (BEB), and
hierarchical triple eclipsing binaries (HEB).  In this work, where
we are concerned with long-period signals, we do not consider the HEB
scenario, as most known hierarchical stellar systems have two components on
relatively short orbits \citep{}.
